Implementing \Kwd{DNS} in \Kwd{C0}

### 2017-12-13 paper.tex
Removed section on NS records from paper.

Moreover, from our testing, it appears that there are more pressing issues to fix with \Kwd{c0ns}. In particular, we ran into some issues while testing in that while we implement all of the resource record types that we expect to get from a client, sometimes we get unexpected resource record types from the remote nameserver that we query. In particular, we do not handle NS resource records, which are used to inform recursive nameservers of which server is authoritative for the query that was made if the remote server is not authoritative. Adding support for these seems to be a much higher priority than adding caching. Additionally, our low performance even on benchmarks that do not benefit at all from caching suggests that perhaps we should focus on performance on unique queries before adding support for caching. In particular, we believe that performance could be greatly improved by adding support for concurrently processing requests, since resolving a query is network-bound (while we wait for the remote server to get back to us), and so should not block CPU-bound tasks like parsing other incoming queries.

>>>>

Moreover, from our testing, it appears that there are more pressing issues to fix with \Kwd{c0ns}. In  particular, our low performance even on benchmarks which do not benefit at all from caching suggests that perhaps we should focus on performance on unique queries before adding support for caching. In particular, we believe that performance could be greatly improved by adding support for concurrently processing requests, since resolving a query is network-bound (while we wait for the remote server to get back to us), and so should not block CPU-bound tasks like parsing other incoming queries.
